---
title: "Lab_8"
author: "E Baker"
date: "11/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(modelsummary)
library(corrplot)
library(here)
library(broom)

```


### Read in slo_homes.csv (from gauchosapce) 

```{r}
homes<- read_csv(here("slo_homes.csv"))
```

### Create a subset w/ 4 cities

Task: create subset called "homes_subset" that only contains:
-SLO
-Atascadero
-Arroyo Grande
-Santa Maria-Orcutt

```{r}
homes_subset<- homes %>%
  filter(City %in% c("San Luis Obispo", "Atascadero", "Arroyo Grande", "Santa Maria-Orcutt"))
```

### A little exploration
Task: create a summary table that has the mean and standard deviation of home prices grouped by city and sale status
```{r, include=FALSE, eval=FALSE}
homes_subset %>%
  group_by(City, Status) %>%
  summarize(mean_price=mean(Price),
                       sd_price= sd(Price),
                       mean_sqft= mean(SqFt))
            
```


Task: explore relationship beteen suqare footage and home price (from homes_subset) in a scatterplot

```{r}
ggplot(data = homes_subset, aes(x=SqFt, y= Price)) + 
  geom_point() +
  geom_smooth(method=lm)
```

### Try a few linear models
Use multiple linear regression models to investigate relathionships between predictor variables and price.

Create 2 permutations of this model:
1) Price ~ City, Bedrooms, Bathrooms, SqFr, Status (lm1)
2) Price ~ City, SqFt, Status (lm2)
3) Try another (lm3)

```{r}
lm1<- lm(Price~ City + Bedrooms + Bathrooms + SqFt + Status, data =homes_subset)
lm2<- lm(Price ~ City + SqFt + Status, data =homes_subset )
lm3<- lm(Price~ City + SqFt, data =homes_subset)

# If I Wanted SLO ti be the reference level, use:
# fct_relevel to specify a new reference level

### new_homes_subset <- fct_relevel<homes_subset$City, "San Luis Obispo"))

```

#WHOOPS


### Explore correlations between quantitiative variables
Task: make a subset called homes_quant (starting from homes_subset) that only contains variables Price - SqFt

```{r}
homes_quant <- homes_subset %>%
  select(Price:SqFt)

homes_cor <- cor(homes_quant)
```



```{r}

```


